---
title: "Plotting Functions for the correlation Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{correlation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7, 
  fig.height = 5,
  warning = FALSE,
  message = FALSE
)
if (!requireNamespace("ggplot2", quietly = TRUE) ||
    !requireNamespace("ggraph", quietly = TRUE) ||
    !requireNamespace("correlation", quietly = TRUE)) {
  knitr::opts_chunk$set(eval = FALSE)
}
```

## Setup

```{r setup}
library(correlation)
library(see)
data(mtcars)
data(iris)
```

## Correlation Matrix

_([related function documentation](https://easystats.github.io/correlation/reference/correlation.html))_

The default output for `correlation()` is a detailed overview including test statistic, p-values and confidence intervals. A shorter summary in matrix-layout can be obtained by using `summary()` or `as.table()`.

```{r}
result <- correlation(iris)

result

as.table(result)
```

The result from `as.table()` can be used to create a plot.
 
```{r}
m <- as.table(result)
plot(m)
```

It is also possible to add correlation coefficients and p-values.

```{r}
plot(m, show_values = TRUE, show_p = TRUE, show_legend = FALSE)
```

## Gaussian Graphical Models (GGMs)

To create a Gaussian Graphical Models plot, the library *ggraph*  needs to be loaded first.

```{r}
library(ggraph)
result <- correlation(mtcars, partial = TRUE)

result

plot(result)
```
