---
title: "Plotting Functions for the 'correlation' Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting Functions for the 'correlation' Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  warning = FALSE,
  message = FALSE
)
if (!requireNamespace("ggplot2", quietly = TRUE) ||
  !requireNamespace("ggraph", quietly = TRUE) ||
  !requireNamespace("poorman", quietly = TRUE) &&
  !packageVersion("correlation") > "0.7.1") {
  knitr::opts_chunk$set(eval = FALSE)
} else {
  library(ggplot2)
  library(ggraph)
  library(poorman)
  library(correlation)
}
```

This vignette can be referred to by citing the package:

```{r}
citation("see")
```

# Introduction

`correlation` is an [**easystats**](https://github.com/easystats/easystats) package focused on correlation analysis. It's lightweight, easy to use, and allows for the computation of many different types of correlation, including:

✅ **Pearson's correlation**<br>
✅ **Spearman's rank correlation**<br>
✅ **Kendall's rank correlation**<br>
✅ **Biweight midcorrelation**<br>
✅ **Distance correlation**<br>
✅ **Percentage bend correlation**<br>
✅ **Shepherd's Pi correlation**<br>
✅ **Blomqvist’s coefficient**<br>
✅ **Hoeffding’s D**<br>
✅ **Gamma correlation**<br>
✅ **Gaussian rank correlation**<br>
✅ **Point-Biserial and biserial correlation**<br>
✅ **Winsorized correlation**<br>
✅ **Polychoric correlation**<br>
✅ **Tetrachoric correlation**<br>
✅ **Multilevel correlation**<br>

An overview and description of these correlations types is [**available here**](https://easystats.github.io/correlation/articles/types.html). Moreover, many of these correlation types are available as **partial** or within a **Bayesian** framework.

# Setup

```{r setup}
library(correlation)
library(see)
library(ggplot2)
data(mtcars)
data(iris)
```


# Correlation Scatterplot

_([related function documentation](https://easystats.github.io/correlation/reference/cor_test.html))_

It is easy to visualize correlation tests with `correlation` and `see`.

```{r}
result <- cor_test(iris, "Sepal.Length", "Petal.Width")

plot(result)
```

We can even customize that to make it more beautiful:

```{r}
plot(result, 
     point = list(aes = list(color = "Petal.Width", size = "Sepal.Length"),
                  alpha = 0.66),
     smooth = list(color = "black", se = FALSE)) +
  see::theme_modern() +
  see::scale_color_material_c(palette = "rainbow", guide = "none") +
  scale_size_continuous(guide = "none")
```


# Correlation Matrix

_([related function documentation](https://easystats.github.io/correlation/reference/correlation.html))_

The default output for `correlation()` is a detailed overview including test
statistic, p-values and confidence intervals. A shorter summary in matrix-layout
can be obtained by using `summary()`.

```{r}
result <- correlation(iris)

result

summary(result)
```

The result from `summary()` can be used to create a plot.

```{r}
s <- summary(result)
plot(s)
```

To change the style of geoms, use the `show_data`-argument.

```{r}
plot(s, show_data = "points")
```


And a "redundant" summary can be plotted as well:

```{r}
s <- summary(result, redundant = TRUE)

s

plot(s)
```

The `corrlation` function also provides a convenient way to change names for selected variables:

```{r, eval=isTRUE(packageVersion("correlation") >= '0.7.0')}
plot(summary(correlation(
  data = select(mtcars, wt, mpg, drat),
  rename = c("weight", "miles per gallon", "rear axle ratio")
)))
```

# Gaussian Graphical Models (GGMs)

To create a Gaussian Graphical Models plot, the library *ggraph* needs to be
loaded first.

```{r}
library(ggraph)
result <- correlation(mtcars, partial = TRUE)

result

plot(result)
```
