---
title:"Plotting Functions for the 'datawizard' Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting Functions for the 'datawizard' Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  warning = FALSE,
  message = FALSE
)

# The following are needed by `{parameters}` for cluster analysis:
# `{factoextra}`, `{mclust}`, and `{NbClust}`
#
# `{httr}` is needed for `insight::download_model()`
can_evaluate <- FALSE
pkgs <- c("datawizard", "ggplot2")
successfully_loaded <- vapply(pkgs, requireNamespace, FUN.VALUE = logical(1L), quietly = TRUE)
all_deps_available <- all(successfully_loaded)

# even if all dependencies are available, evaluate only if internet access is available
if (all_deps_available) {
  can_evaluate <- curl::has_internet()
}

if (can_evaluate) {
  knitr::opts_chunk$set(eval = TRUE)
  vapply(pkgs, require, FUN.VALUE = logical(1L), quietly = TRUE, character.only = TRUE)
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

This vignette can be referred to by citing the package:

```{r}
citation("see")
```

## Introduction

*datawizard* is a lightweight package to easily manipulate, clean, transform, and prepare your data for analysis. Most courses and tutorials about statistical modeling assume that you are working with a clean and tidy dataset. In practice, however, a major part of doing statistical modeling is preparing your data-cleaning up values, creating new columns, reshaping the dataset, or transforming some variables. *datawizard* provides easy to use tools to perform these common, critical, and sometimes tedious data preparation tasks.

For more, see: <https://easystats.github.io/datawizard/>

## Setup and Model Fitting

```{r setup}
library(datawizard)
library(see)
library(ggplot2)
theme_set(theme_modern())
```

## Description of Variable Distributions

_([related function documentation](https://easystats.github.io/datawizard/reference/describe_distribution.html))_

### Histogram for Numbers with Fractional Part

```{r}
data(iris)
result <- describe_distribution(iris$Sepal.Length)
result

plot(result)
```

### Add Range of Dispersion (SD or MAD)

```{r}
plot(result, dispersion = TRUE)
```

### Thin Bars for Integer Values

```{r}
set.seed(333)
x <- sample(1:100, 1000, replace = TRUE)
result <- describe_distribution(x)
result

plot(result)
```

### Use a Normal Curve instead of Ribbon

```{r}
plot(result, dispersion = TRUE, dispersion_style = "curve")
```

### Highlighting Categories

```{r}
set.seed(123)
result <- describe_distribution(sample(LETTERS[1:10], 1000, TRUE))

# highlight one category
plot(result, highlight = "D")

# highlight multiple categories
plot(result, highlight = c("D", "H"), size_bar = 0.4)

# own color scales - pass a named vector to 'scale_fill_manual()'
# the name of the non-highlighted color is "no_highlight".
plot(result, highlight = c("D", "H", "A"), size_bar = 0.4) +
  scale_fill_manual(values = c(D = "red", H = "green", A = "gold", no_highlight = "steelblue"))
```
