---
title: "Plotting Functions for the 'effectsize' Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting Functions for the 'effectsize' Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  warning = FALSE,
  message = FALSE
)

pkgs <- c("effectsize", "ggplot2", "poorman")
successfully_loaded <- vapply(pkgs, requireNamespace, FUN.VALUE = logical(1L), quietly = TRUE)
can_evaluate <- all(successfully_loaded)

if (can_evaluate) {
  knitr::opts_chunk$set(eval = TRUE)
  vapply(pkgs, require, FUN.VALUE = logical(1L), quietly = TRUE, character.only = TRUE)
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

This vignette can be referred to by citing the package:

```{r}
citation("see")
```

# Introduction

The *effectsize* package in *easystats* provides utilities to work with indices of effect size and standardized parameters, allowing computation and conversion of indices such as Cohen’s *d*, *r*, odds-ratios, etc.

For more, see: <https://easystats.github.io/effectsize/>

# Setup

```{r setup}
library(poorman)
library(effectsize)
library(see)
data(mtcars)
data(iris)
```

# Effect size tables

_([related function documentation](https://easystats.github.io/effectsize/reference/eta_squared.html))_

```{r}
aov(mpg ~ factor(am) * factor(cyl), data = mtcars) %>%
  eta_squared() %>%
  plot()


t_to_d(t = c(1, -1.3, -3, 2.3), df_error = c(40, 35, 40, 85)) %>%
  plot()
```

# Equivalence tests

_([related function documentation](https://easystats.github.io/effectsize/reference/equivalence_test.effectsize_table.html))_

```{r}
aov(mpg ~ factor(am) * factor(cyl), data = mtcars) %>%
  eta_squared() %>%
  equivalence_test(range = 0.3) %>%
  plot()


t_to_d(t = c(1, -1.3, -3, 2.3), df_error = c(40, 35, 40, 85)) %>%
  equivalence_test(range = 1) %>%
  plot()
```
