---
title: "Plotting Functions for the 'parameters' Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting Functions for the 'parameters' Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  warning = FALSE,
  message = FALSE
)
if (!requireNamespace("parameters", quietly = TRUE) ||
  !requireNamespace("effectsize", quietly = TRUE) ||
  !requireNamespace("insight", quietly = TRUE) ||
  !requireNamespace("httr", quietly = TRUE) ||
  !requireNamespace("glmmTMB", quietly = TRUE) ||
  !requireNamespace("lme4", quietly = TRUE) ||
  !requireNamespace("brms", quietly = TRUE) ||
  !requireNamespace("lavaan", quietly = TRUE) ||
  !requireNamespace("metafor", quietly = TRUE) ||
  !requireNamespace("ggplot2", quietly = TRUE) ||
  !requireNamespace("splines", quietly = TRUE)) {
  knitr::opts_chunk$set(eval = FALSE)
}
```

## Setup and Model Fitting

```{r setup}
library(parameters)
library(effectsize)
library(insight)
library(see)
library(glmmTMB)
library(lme4)
library(lavaan)
library(metafor)
library(ggplot2)
library(splines)
data("Salamanders")
data("iris")
data("sleepstudy")
data("qol_cancer")

set.seed(12345)
sleepstudy$grp <- sample(1:5, size = 180, replace = TRUE)

theme_set(theme_modern())
```

```{r}
# fit three example model
model1 <- glmmTMB(
  count ~ spp + mined + (1 | site),
  ziformula =  ~mined,
  family = poisson(),
  data = Salamanders
)
model_parameters(model1)


model2 <- lm(Sepal.Length ~ Species * bs(Petal.Width, degree = 2), data = iris)
model_parameters(model2)


model3 <- lmer(
  Reaction ~ Days + (1 | grp) + (1 | Subject),
  data = sleepstudy
)

model4 <- lm(QoL ~ time + age + education, data = qol_cancer)
```

## Model Parameters

_([related function documentation](https://easystats.github.io/parameters/reference/model_parameters.html))_

The `plot()`-method for `model_parameters()` creates a so called “forest plot”.
In case of models with multiple components, parameters are separated into facets
by model component.

```{r}
result <- model_parameters(model1)

plot(result)
```

When `size_text` is given, coefficients and confidence intervals are added to
the plot.

```{r}
plot(result, size_text = 4)
```

This also works for exponentiated coefficients.

```{r, eval=FALSE}
result <- model_parameters(model1, exponentiate = TRUE)
plot(result, size_text = 4)
```

It is also possible to plot only the count-model component. This is done in
`model_parameters()` via the `component` argument. In easystats-functions, the
count-component has the more generic name `"conditional"`.

```{r, eval=FALSE}
result <- model_parameters(model1, exponentiate = TRUE, component = "conditional")
plot(result)
```

As compared to the classical `summary()`-output, `model_parameters()`, and hence
the `plot()`-method, tries to create human readable, prettier parameters names.

```{r}
result <- model_parameters(model2)

plot(result)
```

## Simulated Model Parameters

`simulate_parameters()` computes simulated draws of parameters and their related
indices such as Confidence Intervals (CI) and p-values. Simulating parameter
draws can be seen as a (computationally faster) alternative to bootstrapping.

As `simulate_parameters()` is based on `simulate_model()` and thus simulates
many draws for each parameter, `plot()` will produce similar plots as the
density estimation plots [from Bayesian
models](https://easystats.github.io/see/articles/bayestestR.html).

```{r}
result <- simulate_parameters(model1)

plot(result)
```

```{r}
plot(result, stack = FALSE)
```

To avoid vertical overlapping, use `normalize_height`.

```{r}
plot(result, stack = FALSE, normalize_height = TRUE)
```

```{r fig.height=6, fig.width=8}
plot(result, n_columns = 2)
```

```{r}
plot(result, n_columns = 2, stack = FALSE)
```

## Model Parameters of SEM models

```{r fig.width=9, fig.height=7}
structure <- " visual  =~ x1 + x2 + x3
               textual =~ x4 + x5 + x6
               speed   =~ x7 + x8 + x9 "

model <- lavaan::cfa(structure, data = HolzingerSwineford1939)
result <- parameters::model_parameters(model)
plot(result)
```

## Model Parameters of Bayesian models

`model_parameters()` for Bayesian models will produce "forest plots" (instead of
[density
estimations](https://easystats.github.io/see/articles/bayestestR.html)).

```{r}
# We download the model to save computation time. Here is the code
# to refit the exact model used below...

# zinb <- read.csv("http://stats.idre.ucla.edu/stat/data/fish.csv")
# set.seed(123)
# model <- brm(bf(
#     count ~ persons + child + camper + (1 | persons),
#     zi ~ child + camper + (1 | persons)
#   ),
#   data = zinb,
#   family = zero_inflated_poisson()
# )
brms_model <- insight::download_model("brms_zi_2")
result <- model_parameters(brms_model, effects = "all", component = "all")

plot(result)
```

### Including group levels of random effects

```{r}
result <- model_parameters(brms_model,
  effects = "all",
  component = "all", group_level = TRUE
)
plot(result)
```

### One-column Layout

```{r fig.width=6, fig.height=8}
plot(result, n_column = 1)
```

### Including Intercepts and Variance Estimates for Random Intercepts

```{r fig.width=6, fig.height=8}
plot(result, show_intercept = TRUE)
```

## Model Parameters of Meta-Analysis models

```{r, warning=FALSE, message=FALSE}
mydat <- data.frame(
  effectsize = c(-0.393, 0.675, 0.282, -1.398),
  standarderror = c(0.317, 0.317, 0.13, 0.36)
)

ma <- rma(yi = effectsize, sei = standarderror, method = "REML", data = mydat)
result <- model_parameters(ma)

result
plot(result)
```

If `size_text` is not `NULL`, estimates and confidence intervals are included in
the plot.

```{r, warning=FALSE, message=FALSE}
plot(result, size_text = 4)
```

### Funnel plots

If `type = "funnel"`, a funnel plot is created.

```{r, warning=FALSE, message=FALSE}
plot(result, type = "funnel")
```

### Model Parameters of Meta-Analysis Models with Subgroups

```{r, warning=FALSE, message=FALSE}
set.seed(123)
data(dat.bcg)
dat <- escalc(
  measure = "RR",
  ai = tpos,
  bi = tneg,
  ci = cpos,
  di = cneg,
  data = dat.bcg
)
dat$author <- make.unique(dat$author)
dat$disease <- sample(c("Cancer", "CVD", "Depression"), size = nrow(dat), replace = TRUE)
model <- rma(yi, vi, mods = ~disease, data = dat, digits = 3, slab = author)
result <- model_parameters(model)

result
plot(result)
```

## Bayesian Meta-Analysis using brms

```{r, eval=FALSE}
# We download the model to save computation time. Here is the code
# to refit the exact model used below...

# Data from
# https://github.com/MathiasHarrer/Doing-Meta-Analysis-in-R/blob/master/_data/Meta_Analysis_Data.RData
# set.seed(123)
# priors <- c(prior(normal(0,1), class = Intercept),
#             prior(cauchy(0,0.5), class = sd))
#
# brm(TE|se(seTE) ~ 1 + (1|Author),
#    data = Meta_Analysis_Data,
#    prior = priors,
#    iter = 4000)
library(brms)
model <- insight::download_model("brms_meta_1")
result <- model_parameters(model)

result
plot(result)
```

## Comparison of Models

_([related function documentation](https://easystats.github.io/parameters/reference/compare_parameters.html))_

```{r}
data(iris)
# shorter variable name
iris$Length <- iris$Petal.Length
lm1 <- lm(Sepal.Length ~ Species, data = iris)
lm2 <- lm(Sepal.Length ~ Species + Length, data = iris)
lm3 <- lm(Sepal.Length ~ Species * Length, data = iris)

result <- compare_parameters(lm1, lm2, lm3)
plot(result)
```

```{r fig.width = 8}
plot(result, size_text = 3.8) + 
  labs(y = NULL) + 
  theme(legend.position = "bottom")
```

## Equivalence Testing

_([related function documentation](https://easystats.github.io/parameters/reference/equivalence_test.lm.html))_

### For fixed effects

```{r}
# default rules, like in bayestestR::equivalence_test()
result <- equivalence_test(model4)
result

plot(result)
```

```{r}
result <- equivalence_test(model4, rule = "cet")
result

plot(result)
```

### For random effects

```{r fig.height=8}
result <- equivalence_test(model3, effects = "random")
result

plot(result)
```

### From simulated model parameters

```{r fig.height=8}
simulated_parameters <- simulate_model(model1, component = "conditional")
result <- equivalence_test(simulated_parameters)
result

plot(result)
```

## Principal Component Analysis

_([related function documentation](https://easystats.github.io/parameters/reference/principal_components.html))_

```{r}
data(mtcars)
result <- principal_components(mtcars[, 1:7], n = "all", threshold = 0.2)
result

plot(result)
```

```{r}
result <- principal_components(
  mtcars[, 1:7],
  n = 3,
  rotation = "varimax",
  threshold = "max",
  sort = TRUE
)

result

plot(result, type = "line", text_color = "white") +
  theme_abyss()
```

## Cluster Analysis

_([related function documentation](https://easystats.github.io/parameters/reference/cluster_analysis.html))_

```{r}
data(iris)
result <- cluster_analysis(iris[, 1:4], n_clusters = 3)
result

plot(result)

result <- cluster_analysis(iris[, 1:4], n_clusters = 4)
plot(result, n_columns = 2)
```

## Number of Components/Factors to Retain

_([related function documentation](https://easystats.github.io/parameters/reference/n_factors.html))_

```{r}
data(mtcars)
result <- n_factors(mtcars, type = "PCA")
result

plot(result)
plot(result, type = "line")
```

## Number of Clusters to Retain

_([related function documentation](https://easystats.github.io/parameters/reference/n_clusters.html))_

```{r}
data(iris)
result <- n_clusters(standardize(iris[, 1:4]))
result

plot(result)
plot(result, type = "line")
```

## Description of Variable Distributions

_([related function documentation](https://easystats.github.io/parameters/reference/describe_distribution.html))_

### Histogram for Numbers with Fractional Part

```{r}
data(iris)
result <- describe_distribution(iris$Sepal.Length)
result

plot(result)
```

### Add Range of Dispersion (SD or MAD)

```{r}
plot(result, dispersion = TRUE)
```

### Thin Bars for Integer Values

```{r}
set.seed(333)
x <- sample(1:100, 1000, replace = TRUE)
result <- describe_distribution(x)
result

plot(result)
```

### Use a Normal Curve instead of Ribbon

```{r}
plot(result, dispersion = TRUE, dispersion_style = "curve")
```

### Highlighting Categories

```{r}
set.seed(123)
result <- describe_distribution(sample(LETTERS[1:10], 1000, TRUE))

# highlight one category
plot(result, highlight = "D")

# highlight multiple categories
plot(result, highlight = c("D", "H"), size_bar = .4)

# own color scales - pass a named vector to 'scale_fill_manual()'
# the name of the non-highlighted color is "no_highlight".
plot(result, highlight = c("D", "H", "A"), size_bar = .4) +
  scale_fill_manual(values = c(D = "red", H = "green", A = "gold", no_highlight = "steelblue"))
```
