---
title: "Plotting Functions for the 'performance' Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{performance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  dpi = 300,
  out.width = "100%",
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  warning = FALSE,
  message = FALSE
)
```

```{r setup}
library(performance)
library(lme4)
library(see)
```

# Checking Model Assumptions

## Binned Residuals

_([related function documentation](https://easystats.github.io/performance/reference/binned_residuals.html))_

Example where model is **not** a good fit.

```{r message=TRUE}
model <- glm(vs ~ wt + mpg, data = mtcars, family = "binomial")
binned_residuals(model)
```

Example where model **is** a good fit.

```{r message=TRUE}
mod <- glm(am ~ mpg + vs + cyl, family = binomial(), data = mtcars)
binned_residuals(mod)
```

## Check for Multicollinearity - Variance Inflation Factor

_([related function
documentation](https://easystats.github.io/performance/reference/check_collinearity.html))_

```{r}
m <- lm(mpg ~ wt + cyl + gear + disp, data = mtcars)
result <- check_collinearity(m)

result
plot(result)
```

```{r}
library(glmmTMB)
data(Salamanders)

# create highly correlated pseudo-variable
set.seed(1)
Salamanders$cover2 <-
  Salamanders$cover * runif(n = nrow(Salamanders), min = .7, max = 1.5)

# fit mixed model with zero-inflation
model <- glmmTMB(
  count ~ spp + mined + cover + cover2 + (1 | site),
  ziformula = ~ spp + mined,
  family = truncated_poisson,
  data = Salamanders
)

result <- check_collinearity(model)

result
plot(result)
```

## Check for Outliers

_([related function documentation](https://easystats.github.io/performance/reference/check_outliers.html))_

```{r}
# select only mpg and disp (continuous)
mt1 <- mtcars[, c(1, 3, 4)]
# create some fake outliers and attach outliers to main df
mt2 <- rbind(mt1, data.frame(mpg = c(37, 40), disp = c(300, 400), hp = c(110, 120)))
# fit model with outliers
model <- lm(disp ~ mpg + hp, data = mt2)
result <- check_outliers(model)

result
plot(result)
```

## Check for Normal Distributed Residuals

_([related function documentation](https://easystats.github.io/performance/reference/check_normality.html))_

```{r}
model <- lm(mpg ~ wt + cyl + gear + disp, data = mtcars)
result <- check_normality(model)
```

### Density Plot

```{r}
plot(result)
```

### QQ Plot

```{r}
plot(result, type = "qq")
```

### PP Plot

```{r}
plot(result, type = "pp")
```

## Check for Normal Distributed Random Effects

_([related function documentation](https://easystats.github.io/performance/reference/check_normality.html))_

```{r}
model <- lmer(Reaction ~ Days + (Days | Subject), sleepstudy)
result <- check_normality(model, effects = "random")
plot(result)
```

## Check for Heteroscedasticity

_([related function documentation](https://easystats.github.io/performance/reference/check_heteroscedasticity.html))_

```{r}
model <- lm(mpg ~ wt + cyl + gear + disp, data = mtcars)
result <- check_heteroscedasticity(model)
plot(result)
```

## Check for Homogeneity

_([related function documentation](https://easystats.github.io/performance/reference/check_homogeneity.html))_

```{r}
model <- lm(len ~ supp + dose, data = ToothGrowth)
result <- check_homogeneity(model)
plot(result)
```

## Posterior Predictive Checks

_([related function documentation](https://easystats.github.io/performance/reference/pp_check.html))_

```{r}
model <- lm(mpg ~ wt + cyl + gear + disp, data = mtcars)
pp_check(model)
```

To check if the model properly captures the variation in the data, use
`check_range = TRUE`:

```{r}
model <- lm(mpg ~ wt + cyl + gear + disp, data = mtcars)
pp_check(model, check_range = TRUE)
```

# Overall Model Check

_([related function documentation](https://easystats.github.io/performance/reference/check_model.html))_

```{r fig.height=12, fig.width=10}
model <- lmer(Reaction ~ Days + (Days | Subject), sleepstudy)
check_model(model)
```

```{r}
check_model(model, panel = FALSE)
```

Note that not all checks supported in `performance` will be reported in this
unified **visual** check. For example, for linear models, one needs to check the
assumption that errors are not autocorrelated, but this check will not be shown
in the visual check.

```{r message=TRUE}
check_autocorrelation(lm(formula = wt ~ mpg, data = mtcars))
```

# Compare Model Performances

_([related function documentation](https://easystats.github.io/performance/reference/model_performance.html))_

`compare_performance()` computes indices of model performance for different
models at once and hence allows comparison of indices across models. The
`plot()`-method creates a "spiderweb" plot, where the different indices are
normalized and larger values indicate better model performance. Hence, points
closer to the center indicate worse fit indices.

```{r}
data(iris)
lm1 <- lm(Sepal.Length ~ Species, data = iris)
lm2 <- lm(Sepal.Length ~ Species + Petal.Length, data = iris)
lm3 <- lm(Sepal.Length ~ Species * Sepal.Width, data = iris)
lm4 <- lm(Sepal.Length ~ Species * Sepal.Width + Petal.Length + Petal.Width, data = iris)
result <- compare_performance(lm1, lm2, lm3, lm4)

result

plot(result)
```

# Model and Vector Properties

_([related function documentation](https://easystats.github.io/performance/reference/check_distribution.html))_

```{r}
model <- lmer(Reaction ~ Days + (Days | Subject), sleepstudy)
result <- check_distribution(model)

result
plot(result)
```

```{r}
vec <- bayestestR::distribution_poisson(n = 500, lambda = 2.5)
result <- check_distribution(vec)

result
plot(result)
```

# ROC curves

_([related function documentation](https://easystats.github.io/performance/reference/performance_roc.html))_

```{r}
if (packageVersion("performance") > "0.7.0") {
data(iris)
set.seed(123)
iris$y <- rbinom(nrow(iris), size = 1, .3)

folds <- sample(nrow(iris), size = nrow(iris) / 8, replace = FALSE)
test_data <- iris[folds, ]
train_data <- iris[-folds, ]

model <- glm(y ~ Sepal.Length + Sepal.Width, data = train_data, family = "binomial")
result <- performance_roc(model, new_data = test_data)

result
plot(result)
}
```
