---
title: "Color Scales for Dark Themes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Color Scales for Dark Themes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 5.5,
  warning = FALSE,
  message = FALSE
)

if (!requireNamespace("patchwork", quietly = TRUE)) {
  knitr::opts_chunk$set(eval = FALSE)
}
```

This vignette can be referred to by citing the package:

```{r}
citation("see")
```

Before we start, we create some data sets with three, four and five groups; one
is useful to demonstrate line-geoms, the iris-dataset is used for point-geoms.

```{r setup}
library(ggplot2)
library(see)

data(iris)
iris$group4 <- as.factor(sample(1:4, size = nrow(iris), replace = TRUE))
iris$group5 <- as.factor(sample(1:5, size = nrow(iris), replace = TRUE))

d1 <- data.frame(
  x = rep(1:20, 3),
  y = c(
    seq(2, 4, length.out = 20),
    seq(3, 6, length.out = 20),
    seq(5, 3, length.out = 20)
  ),
  group = rep(factor(1:3), each = 20)
)

d2 <- data.frame(
  x = rep(1:20, 4),
  y = c(
    seq(2, 4, length.out = 20),
    seq(3, 6, length.out = 20),
    seq(5, 3, length.out = 20),
    seq(4, 2.5, length.out = 20)
  ),
  group = rep(factor(1:4), each = 20)
)

d3 <- data.frame(
  x = rep(1:20, 5),
  y = c(
    seq(2, 4, length.out = 20),
    seq(3, 6, length.out = 20),
    seq(5, 3, length.out = 20),
    seq(4, 2.5, length.out = 20),
    seq(3.5, 4.5, length.out = 20)
  ),
  group = rep(factor(1:5), each = 20)
)

theme_set(theme_abyss(legend.position = "bottom"))
```

# The *see* Color Scales

There are several different [color scales available](https://easystats.github.io/see/reference/index.html#section-scales)
in the *see* package, most of them having some pre-defined palettes like
`"full"`, `"ice"`, `"rainbow"`, `"complement"`, `"contrast"`, or `"light"` -
exceptions are the [pizza color scale](https://easystats.github.io/see/reference/scale_color_pizza.html) and
[bluebrown color scale](https://easystats.github.io/see/reference/scale_color_blubrown.html).

In this vignettes, we show the `"light"` palettes for the different color scales
to give an impression how these scales work with different type of data,
especially for *dark themes*.

## Social Colors - Three Groups

```{r}
p1 <- ggplot(d1, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_social(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = Species)) +
  geom_point2(size = 2.5) +
  scale_color_social(palette = "light")

plots(p1, p2, n_rows = 1)
```

## Social Colors - Four Groups

```{r}
p1 <- ggplot(d2, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_social(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group4)) +
  geom_point2(size = 2.5) +
  scale_color_social(palette = "light")

plots(p1, p2, n_rows = 1)
```

## Social Colors - Five Groups

```{r}
p1 <- ggplot(d3, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_social(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group5)) +
  geom_point2(size = 2.5) +
  scale_color_social(palette = "light")

plots(p1, p2, n_rows = 1)
```

# Material Colors

## Material Colors - Three Groups

```{r}
p1 <- ggplot(d1, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_material(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = Species)) +
  geom_point2(size = 2.5) +
  scale_color_material(palette = "light")

plots(p1, p2, n_rows = 1)
```

## Material Colors - Four Groups

```{r}
p1 <- ggplot(d2, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_material(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group4)) +
  geom_point2(size = 2.5) +
  scale_color_material(palette = "light")

plots(p1, p2, n_rows = 1)
```

## Material Colors - Five Groups

```{r}
p1 <- ggplot(d3, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_material(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group5)) +
  geom_point2(size = 2.5) +
  scale_color_material(palette = "light")

plots(p1, p2, n_rows = 1)
```

# Flat Colors

## Flat Colors - Three Groups

```{r}
p1 <- ggplot(d1, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_flat(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = Species)) +
  geom_point2(size = 2.5) +
  scale_color_flat(palette = "light")

plots(p1, p2, n_rows = 1)
```

## Flat Colors - Four Groups

```{r}
p1 <- ggplot(d2, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_flat(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group4)) +
  geom_point2(size = 2.5) +
  scale_color_flat(palette = "light")

plots(p1, p2, n_rows = 1)
```

## Flat Colors - Five Groups

```{r}
p1 <- ggplot(d3, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_flat(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group5)) +
  geom_point2(size = 2.5) +
  scale_color_flat(palette = "light")

plots(p1, p2, n_rows = 1)
```

# Metro Colors

## Metro Colors - Three Groups

```{r}
p1 <- ggplot(d1, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_metro(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = Species)) +
  geom_point2(size = 2.5) +
  scale_color_metro(palette = "light")

plots(p1, p2, n_rows = 1)
```

## Metro Colors - Four Groups

```{r}
p1 <- ggplot(d2, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_metro(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group4)) +
  geom_point2(size = 2.5) +
  scale_color_metro(palette = "light")

plots(p1, p2, n_rows = 1)
```

## Metro Colors - Five Groups

```{r}
p1 <- ggplot(d3, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_metro(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group5)) +
  geom_point2(size = 2.5) +
  scale_color_metro(palette = "light")

plots(p1, p2, n_rows = 1)
```

# See Colors

## See Colors - Three Groups

```{r}
p1 <- ggplot(d1, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_see(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = Species)) +
  geom_point2(size = 2.5) +
  scale_color_see(palette = "light")

plots(p1, p2, n_rows = 1)
```

## See Colors - Four Groups

```{r}
p1 <- ggplot(d2, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_see(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group4)) +
  geom_point2(size = 2.5) +
  scale_color_see(palette = "light")

plots(p1, p2, n_rows = 1)
```

## See Colors - Five Groups

```{r}
p1 <- ggplot(d3, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_see(palette = "light")

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group5)) +
  geom_point2(size = 2.5) +
  scale_color_see(palette = "light")

plots(p1, p2, n_rows = 1)
```

# Pizza Colors

## Pizza Colors - Three Groups

```{r}
p1 <- ggplot(d1, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_pizza()

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = Species)) +
  geom_point2(size = 2.5) +
  scale_color_pizza()

plots(p1, p2, n_rows = 1)
```

## Pizza Colors - Four Groups

```{r}
p1 <- ggplot(d2, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_pizza()

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group4)) +
  geom_point2(size = 2.5) +
  scale_color_pizza()

plots(p1, p2, n_rows = 1)
```

## Pizza Colors - Five Groups

```{r}
p1 <- ggplot(d3, aes(x, y, colour = group)) +
  geom_line(size = 1) +
  scale_color_pizza()

p2 <- ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = group5)) +
  geom_point2(size = 2.5) +
  scale_color_pizza()

plots(p1, p2, n_rows = 1)
```

# Overview of Palette Colors

```{r fig.height=12,echo=FALSE}
theme_set(theme_minimal())

d <- data.frame(
  x = names(social_colors())
)

p1 <- ggplot(d, aes(x, fill = x)) +
  geom_bar(width = 0.9) +
  scale_fill_manual(values = social_colors()) +
  scale_y_continuous(labels = NULL, expand = c(0, 0)) +
  guides(fill = "none") +
  ylab(NULL) +
  xlab(NULL) +
  theme(
    axis.text.x = element_text(angle = 90),
    panel.grid = element_blank()
  )



d <- data.frame(
  x = names(flat_colors())
)

p2 <- ggplot(d, aes(x, fill = x)) +
  geom_bar(width = 0.9) +
  scale_fill_manual(values = flat_colors()) +
  scale_y_continuous(labels = NULL, expand = c(0, 0)) +
  guides(fill = "none") +
  ylab(NULL) +
  xlab(NULL) +
  theme(
    axis.text.x = element_text(angle = 90),
    panel.grid = element_blank()
  )

d <- data.frame(
  x = names(material_colors())
)

p3 <- ggplot(d, aes(x, fill = x)) +
  geom_bar(width = 0.9) +
  scale_fill_manual(values = material_colors()) +
  scale_y_continuous(labels = NULL, expand = c(0, 0)) +
  guides(fill = "none") +
  ylab(NULL) +
  xlab(NULL) +
  theme(
    axis.text.x = element_text(angle = 90),
    panel.grid = element_blank()
  )



d <- data.frame(
  x = names(metro_colors())
)

p4 <- ggplot(d, aes(x, fill = x)) +
  geom_bar(width = 0.9) +
  scale_fill_manual(values = metro_colors()) +
  scale_y_continuous(labels = NULL, expand = c(0, 0)) +
  guides(fill = "none") +
  ylab(NULL) +
  xlab(NULL) +
  theme(
    axis.text.x = element_text(angle = 90),
    panel.grid = element_blank()
  )


d <- data.frame(
  x = names(see_colors())
)

p5 <- ggplot(d, aes(x, fill = x)) +
  geom_bar(width = 0.9) +
  scale_fill_manual(values = see_colors()) +
  scale_y_continuous(labels = NULL, expand = c(0, 0)) +
  guides(fill = "none") +
  ylab(NULL) +
  xlab(NULL) +
  theme(
    axis.text.x = element_text(angle = 90),
    panel.grid = element_blank()
  )


d <- data.frame(
  x = names(pizza_colors())
)

p6 <- ggplot(d, aes(x, fill = x)) +
  geom_bar(width = 0.9) +
  scale_fill_manual(values = pizza_colors()) +
  scale_y_continuous(labels = NULL, expand = c(0, 0)) +
  guides(fill = "none") +
  ylab(NULL) +
  xlab(NULL) +
  theme(
    axis.text.x = element_text(angle = 90),
    panel.grid = element_blank()
  )


d <- data.frame(
  x = names(bluebrown_colors())
)

p7 <- ggplot(d, aes(x, fill = x)) +
  geom_bar(width = 0.9) +
  scale_fill_manual(values = bluebrown_colors()) +
  scale_y_continuous(labels = NULL, expand = c(0, 0)) +
  guides(fill = "none") +
  ylab(NULL) +
  xlab(NULL) +
  theme(
    axis.text.x = element_text(angle = 90),
    panel.grid = element_blank()
  )


plots(p1, p2, p3, p4, p5, p6, p7, n_columns = 1, tags = c("Social", "Flat", "Material", "Metro", "See", "Pizza", "Bluebrown"))
```
