---
title: "see: R Package for Visualizing Statistical Models"
tags:
  - R
  - easystats
  - ggplot2
  - ggplot2-extension
authors:
- affiliation: 1
  name: Daniel Lüdecke
  orcid: 0000-0002-8895-3206
- affiliation: 2
  name: Mattan S. Ben-Shachar
  orcid: 0000-0002-4287-4801
- affiliation: 3
  name: Indrajeet Patil
  orcid: 0000-0003-1995-6531
- affiliation: 4
  name: Brenton M. Wiernik
  orcid: 0000-0001-9560-6336
- affiliation: 5
  name: Philip Waggoner
  orcid: 0000-0002-7825-7573
- affiliation: 6
  name: Dominique Makowski
  orcid: 0000-0001-5375-9967
affiliations:
- index: 1
  name:  University Medical Center Hamburg-Eppendorf, Germany
- index: 2
  name: Ben-Gurion University of the Negev, Israel
- index: 3
  name: Center for Humans and Machines, Max Planck Institute for Human Development, Berlin, Germany
- index: 4
  name: Department of Psychology, University of South Florida, USA 
- index: 5
  name: University of Chicago, USA
- index: 6
  name: Nanyang Technological University, Singapore
date: "`r Sys.Date()`"
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
link-citations: yes
---

```{r, warning=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  dpi = 450,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

# Summary

*Easystats* is a collection of packages that operate in synergy to provide a consistent and intuitive syntax when working with statistical models in the R programming language [@base2021]. Though most of the packages return comprehensive numeric summaries of model parameters and performance, the ability to visulaize model output leads to more informative, well-rounded scientific reporting. As a core member of the *easystats* ecosystem and built on top of *ggplot2*, the *see* package offers a host of functions and tools for a range of publication-ready statistical visualizations.

# Statement of Need

A number of data visualization tools built on *ggplot2* [@Wickham2016] exist for graphically exploring statistical models^[For a sampling of these packages, see: <https://exts.ggplot2.tidyverse.org/gallery/>]. A few of these packages provide ready-made plots or geometric layers for conveniently preparing common visualizations, but without linking them to any particular statistical analyses (e.g., *ggrepel*, *ggalluvial*, *ggridges*, *ggdist*, etc.). A few other packages *do* provide visualizations linked to particular statistical analyses (e.g., *ggpubr*, *tidymv*, *ggstatsplot*, *survminer*, etc.), but they tend to be more specialized. For example, the *ggstatsplot* package [@Patil2021] offers visualizations only for statistical analysis of one-way factorial designs, and the *plotmm* package [@Waggoner2020] offers *ggplot2* visualizations of specific types of mixture model objects. 

The *see* package, on the other hand, is designed to work with a wide range of statistical models and provides a more comprehensive *ggplot2*-based visualization toolbox corresponding with all stages of statistical analysis, from model fitting to reporting. Additionally, as a core member of the *easystats* ecosystem, *see* is built upon, and in line with, the common syntax and philosophy of the ecosystem. The result is an efficient package with consistent syntax that minimizes the barrier to producing high-quality statistical visualizations in R.

# Features

Though we introduce only one plotting method for each *easystats* package, many other methods are available. Interested readers are encouraged to explore the range of examples on the package website, <https://easystats.github.io/see/>.

## Visualizing parameters of a model

The *parameters* package converts regression model objects into dataframes [@Lüdecke2020parameters]. The *see* package can take this transformed object and, for example, create a dot-and-whisker plot for the extracted regression estimates simply by passing the `parameters` class object to `plot()`.

```{r}
library(parameters)
library(see)

mod <- lm(wt ~ am * cyl, mtcars)

plot(parameters(mod))
```

Similarly, for Bayesian regression model objects, which are handled by the *bayestestR* package [@Makowski2019], the *see* package can also provide special plotting methods relevant only for Bayesian models (e.g., Highest Density Interval, or *HDI*). Similarly, users can fit the model and pass the model results, extracted via `bayestestR`, to `plot()`.

```{r}
library(bayestestR)
library(rstanarm)
library(see)

mod <- stan_glm(wt ~ mpg, data = mtcars, refresh = 0)
result <- hdi(mod, ci = c(0.5, 0.75, 0.89, 0.95))

plot(result)
```

## Visualizing model fit 

The *performance* package is primarily concerned with checking regression model assumptions [@Lüdecke2020performance]. The *see* package offers a number of tools to visualize these assumption checks, such as the normality of residuals. Similar to uses of *see* with *parameters* introduced in the previous section, users simply pass the fit model object to the relevant *performance* function (`check_normality()` in the example below). Then, this result can be passed to `plot()` to render a *ggplot2* visualization of the check on the normality of the residuals.

```{r}
library(performance)
library(see)

mod <- lm(wt ~ mpg, mtcars)

plot(check_normality(mod))

# or equivalently
check <- check_normality(mod)

plot(check)
```

## Visualizing effect sizes

In addition to providing tabular summaries of regression model objects, the *easystats* ecosystem also provides several packages to assess various aspects of statistical models. Of note, the *effectsize* package assesses the practical importance of observed effects by computing appropriate effect size measures [@Ben-Shachar2020]. In conjunction with *see*, users are able to visualize the magnitude and uncertainty of effect sizes by passing the model object to the relevant `effectsize` function (`omega_squared()` in the following example), and then to `plot()` as before.

```{r}
library(effectsize)
library(see)

mod <- aov(wt ~ am * cyl, mtcars)

plot(omega_squared(mod))
```

## Visualizing marginal effects

The *modelbased* package computes a range of quantities from fit regression models [@Makowski2020modelbased]. With minimal and human-readable code, users start by passing the model object to the relevant *modelbased* function(s) (`estimate_contrasts()` and `estimate_means()` in the example to follow). Then, these new objects containing the *modelbased* quantities are then passed to `plot()` from the *see* package. Of note, in the following example *two* quantities (objects `contrasts` and `means`) are passed to `plot()`, demonstrating and deepening the flexibility of the package.

```{r}
library(modelbased)
library(see)

mod <- stan_glm(wt ~ as.factor(cyl), data = mtcars, refresh = 0)
contrasts <- estimate_contrasts(mod)
means <- estimate_means(mod)

plot(contrasts, means)
```

## Visualizing correlation matrices

The *correlation* package provides a unified syntax and human-readable code to carry out many flavors of correlation analysis [@Makowski2020]. Results from the `correlation()` function call of class `easycorrelation` are passed to `plot()` from *see* to render these correlations in a matrix.

```{r}
library(correlation)
library(see)

result <- correlation(iris, type = "percentage")

plot(summary(result))
```

# Licensing and Availability

*see* is licensed under the GNU General Public License (v3.0), with all source code openly developed and stored at GitHub (<https://github.com/easystats/see>), along with a corresponding issue tracker for bug reporting and feature enhancements. In the spirit of honest and open science, we encourage requests, tips for fixes, feature updates, as well as general questions and concerns via direct interaction with contributors and developers.

# Acknowledgments

*see* is part of the collaborative [*easystats*](https://github.com/easystats/easystats) ecosystem. Thus, we thank the [members of easystats](https://github.com/orgs/easystats/people) as well as the users.

# References


